Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-05-08 appendix.tex
first version with vn appendix

% !TEX root = paper.tex
\appendix
\section{Model comparisons of the Individual flow harmonics $v_n$}
As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics. Therefore it is important to check how well the individual flow harmonics $v_n$ are produced in the theoretical models used in Sec~\ref{sec:theory}.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v2.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v3.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/hydrocom_v4.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
        \label{fig:Figure_8}
              \end{center}
\end{figure*}

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v2.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v3.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v4.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
        \label{fig:Figure_9}
              \end{center}
\end{figure*}

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v2.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v3.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/amptcom_v4.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various AMPT models.}
        \label{fig:Figure_10}
              \end{center}
\end{figure*}

>>>>

% !TEX root = paper.tex
\appendix
\section{Model comparisons of the Individual flow harmonics $v_n$}
\label{sec:vn}
As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics. Therefore it is important to check how well the individual flow harmonics $v_n$ are produced in the theoretical models used in Sec~\ref{sec:theory}.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_comp_EKRT.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_comp_EKRT.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_comp_EKRT.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}. The lines are hydrodynamic predictions with two different $\eta/s(T)$ parameterizations, labeled in the same way as in ~\cite{Niemi:2015qia}.}
        \label{fig:Figure_8}
              \end{center}
\end{figure*}

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_comp_VISH.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_comp_VISH.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_comp_VISH.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
        \label{fig:Figure_9}
              \end{center}
\end{figure*}

@@

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v2_comp_AMPT.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v3_comp_AMPT.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/v4_comp_AMPT.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various AMPT models.}
        \label{fig:Figure_10}
              \end{center}
\end{figure*}

### 2017-05-08 longSC.tex
to PC
first version with vn appendix

\section{Introduction}

%\textbf{{[A general history on HI]}}

The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP). 
%This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
The matter produced in a heavy-ion collision exhibits strong collective radial expansion. Due to anisotropic pressure gradients in the plane transverse to the beam direction, more particles emitted in the direction of the largest gradients result in anisotropic transverse flow.
The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}. The measurements are well described by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
%and microscopic transport models ~\cite{Xu:2007jv}.  
These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of the QGP in heavy-ion collisions at RHIC and LHC energies is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de}.

@@

\newpage

%\input{appendix.tex}

>>>>

\section{Introduction}
\label{sec:intro}
The main emphasis of the ultra-relativistic heavy-ion collision programs at the Relativistic Heavy Ion Collider (RHIC) and the Large Hadron Collider (LHC) is to study the deconfined phase of strongly interacting nuclear matter, the Quark-Gluon Plasma (QGP). 
%This matter exhibits strong anisotropic flow in the plane transverse to the beam direction, which is driven by anisotropic pressure gradients, resulting in more particles emitted in the direction of the largest gradients.
The matter produced in a heavy-ion collision exhibits strong collective radial expansion. Due to anisotropic pressure gradients in the plane transverse to the beam direction, more particles emitted in the direction of the largest gradients result in anisotropic transverse flow.
The large elliptic flow discovered at RHIC energies~\cite{Ackermann:2000tr} is also observed at LHC energies~\cite{Aamodt:2010pa,Adam:2016izf}. The measurements are well described by calculations utilizing viscous hydrodynamics~\cite{Romatschke:2007mq,Shen:2011eg,Schenke:2011zz,Bozek:2012qs,Gale:2012rq,Hirano:2010je}.
%and microscopic transport models ~\cite{Xu:2007jv}.  
These calculations also demonstrated that the shear viscosity to the entropy density ratio ($\eta/s$) of the QGP in heavy-ion collisions at RHIC and LHC energies is close to a universal lower bound $1/4\pi$~\cite{Kovtun:2004de}.

@@
